Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-10-14 paper.tex
update figures befor sending to Elton

%
%
Using these relations, we show the calculated
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$ in the bottom panels of
Figure \ref{fig-1}b and \ref{fig-1}c, respectively.  In contrast to
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
reach convergence when $L$ exceeds 10 \AA and 15 \AA,
respectively. Such result is in good agreement with the spatially
localized induced dipole moment of a 2D materials as shown in
Supplementary Figure~\ref{SI-fig:rho-profile}.
%
%
Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
panels in Figure\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$
(Figure \ref{fig-1}\textbf{d}-\textbf{e}).
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
%\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Such relations can also be used to remove the dependence on $L$ for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
lattice-independent electronic polarizability
$\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
respectively (details see Supplementary Section \ref{SI-ssec:gw}).
%
% 
% 
% 
% 
These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
of the dielectric properties of 2D materials. In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
More discussions about the choice of the
2D polarizability, comparison with other methods, simulations at the
frequency-dependent domain can be found in Supplementary Section
\ref{SI-ssec:gw}.

@@

Apart from the 2D electronic polarizability proposed here, it is worth
mentioning that a widely-used approach in literature is to treat the
2D material as a slab with an effective dielectric tensor
$\varepsilon_{\mathrm{2D}}$ and thickness $\delta_{\mathrm{2D}}$. Such
method can be found in both experimental and theoretical studies, such
as to interpret ellipsometry data
\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance /
transmission spectra \cite{Li_2014, Yoffe-Wilson69}, optical
conductance \cite{Matthes_2016} and many-body interactions
\cite{Sohier_2016,Meckbach_2018} of 2D materials. The effective
dielectric model allowing applying physical laws of bulk systems
directly to 2D materials using $\varepsilon_{\mathrm{2D}}$. However,
there are several drawbacks of such approach, first of all, the
wavevector($q$)-dependency of dielectric screening in 2D
sheets~\cite{Cudazzo_2011_screening_2D,Olsen_2016_hydrogen,Trolle_2017_eps_subst}
is not captured. More severely, here we show that, due to the
uncertainty of $\delta_{\mathrm{2D}}$, the calculated
$\varepsilon_{\mathrm{2D}}$, in particular its out-of-plane component,
is extremely sensitive to the choice of $\delta_{\mathrm{2D}}$, making
such model questionable.

The basic assumption of the effective dielectric model (EDM) can be
seen in Figure~\ref{fig-emt}\textbf{a}, where the macroscopic
$\varepsilon_{\mathrm{SL}}$ is considered to be contributed by (i) a
2D slab with effective dielectric constant $\varepsilon_{\mathrm{2D}}$
and thickness $\delta_{\mathrm{2D}}$ and (ii) vacuum spacing with
distance $L-\delta_{\mathrm{2D}}$. Using the effective medium theory
(EMT)~\cite{Aspnes_1982,Markel_2016}, the relation between
$\varepsilon_{\mathrm{SL}}$ and $\varepsilon_{\mathrm{2D}}$ can be
expressed using capacitance-like
equations~\cite{Matthes_2016,Laturia_2018} :
\begin{subequations}
  \begin{eqnarray}
    \label{eq:emt-1}
    {\displaystyle \varepsilon_{\mathrm{SL}}^{\parallel}} &= {\displaystyle \frac{\delta_{\mathrm{2D}}}{L} \varepsilon_{\mathrm{2D}}^{\parallel} + \left(1 - \frac{\delta_{\mathrm{2D}}}{L} \right)}\\
     \label{eq:emt-2}
    {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}} &= {\displaystyle \frac{\delta_{\mathrm{2D}}}{L} \frac{1}{\varepsilon_{\mathrm{2D}}^{\perp}} + \left(1 - \frac{\delta_{\mathrm{2D}}}{L} \right)}
  \end{eqnarray}
\end{subequations}
In principle, both the values of $\varepsilon_{\mathrm{2D}}$ and
$\delta_{\mathrm{2D}}$ are unknown for a certain 2D material. To
minimize the modeling error, we used non-linear least-square fitting
to extract $\varepsilon_{\mathrm{2D}}$ and $\delta_{\mathrm{2D}}$ of
selected 2H TMDCs simultaneously from \textit{ab initio}
$\varepsilon_{\mathrm{SL}}$ -- $L$ data in
Figure~\ref{fig-1}\textbf{b} and \ref{fig-1}\textbf{b} (details see
Supplementary Figure~\ref{SI-fig:rescale-prb}). The fitted values of
the slab thickness, $\delta_{\mathrm{2D}}^{\parallel, \mathrm{fit}}$
and $\delta_{\mathrm{2D}}^{\perp, \mathrm{fit}}$ from in-plane and
out-of-plane data, respectively, are shown in Supplementary
Table~\ref{SI-tab:delta-L-DFt}. As seen in Figure
\ref{fig-emt}\textbf{b}, the estimation error of the thickness
estimated from different directions is around 0.06$\sim{}$0.27
\AA{}. Although such uncertainty only corresponds to about
1$\sim{}$4\% of the interlayer spacing in the bulk counterparts of
these 2D materials, its influence on the calculated values
$\varepsilon_{\mathrm{2D}}^{\parallel}$ and
$\varepsilon_{\mathrm{2D}}^{\perp}$ is significant. We estimated the
dispersion of $\varepsilon_{\mathrm{2D}}^{\parallel}$ and
$\varepsilon_{\mathrm{2D}}^{\perp}$ if $\delta_{\mathrm{2D}}$ deviates
from the best fitted value by $\pm{}$2.5 \AA{}, as shown in Figures
\ref{fig-emt}\textbf{c} and \ref{fig-emt}\textbf{d},
respectively. $\varepsilon_{\mathrm{2D}}^{\parallel}$ decays linearly
with $\delta_{\mathrm{2D}}$ with a uncertainty of $\sim{}$10\%, while
strikingly, the value $\varepsilon_{\mathrm{2D}}^{\perp}$ spans over
more than one order of magnitude. The sensitivity of
$\varepsilon_{\mathrm{2D}}^{\perp}$ to $\delta_{\mathrm{2D}}$ explains
the discrepancy in literature that both isotropic~\cite{Sohier_2016}
and highly anisotropic~\cite{Matthes_2016,Laturia_2018}
$\varepsilon_{\mathrm{2D}}$ tensors for 2D materials under the EDM are
reported. As a consequence, the estimated values of
$\varepsilon_{\mathrm{2D}}$, in particular its out-of-plane component,
is highly questionable.

On the contrary, the proposed $\alpha_{\mathrm{2D}}$ approach does not
suffer from such deficiencies, despite its relatively simple
formalism. The relative uncertainty of $\alpha_{\mathrm{2D}}$ is
generally at the order of 10\textsuperscript{-4} (Supplementary Figure
{\color{red} XX}). In addition, the calculation of
$\alpha_{\mathrm{2D}}$ technically simpler than
$\varepsilon_{\mathrm{2D}}$: (i) $\alpha_{\mathrm{2D}}$ can be
achieved using single-point calculation of macroscopic dielectric
tensor, while $\varepsilon_{\mathrm{2D}}$ requires non-linear fitting
of multiple $\varepsilon_{\mathrm{SL}}$ -- $L$ data points; (ii) the
values of $\alpha_{\mathrm{2D}}$ typically converge well for large $L$
($>$20 \AA{}), while $\varepsilon_{\mathrm{2D}}$ suffers from the
uncertainty as described above.

@@

For bulk materials, pioneering works from the 1950s have demonstrated
empirical equations between $\varepsilon$ and the bandgap
$E_{\mathrm{g}}$, including the
Moss~\cite{Moss_1950_relation,Moss_1985_n_Eg,Finkenrath_1988} or
Ravindra~\cite{Ravindra_1980_model,Ravindra_1979_eps_Eg} relations.
Such universal relations, if exist in the context of
$\alpha_{\mathrm{2D}}$, would be of high importance for studying and
predicting the screening of 2D materials.  Inspired by the random
phase approximation (RPA) theory \cite{Adler_1962} within the
$\mathbf{k} \cdot \mathbf{p}$
formalism\cite{kittel_2005_introduction,Jiang_2017_Eg_Eb}, we propose the universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$,
depending on the electronic and geometric information of a 2D material (see
Supplementary Section \ref{SI-sec:theory-1} for details):
% \begin{subequations}
% \begin{eqnarray}
% \label{eq:2D-Moss-para}
  % &\alpha_{\mathrm{2D}}^{\parallel} &=C^{\parallel} E_{g}^{-1} \\
  % \label{eq:2D-Moss-perp}
  % &\alpha_{\mathrm{2D}}^{\perp} & =C^{\perp} \hat{\delta}_{\mathrm{2D}}
% \end{eqnarray}
% \end{subequations}
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &E_{\mathrm{g}} &= C^{\parallel} \alpha_{\mathrm{2D}}^{\parallel} \\
  \label{eq:2D-Moss-perp}
  &\hat{\delta}_{\mathrm{2D}} & = C^{\perp} \alpha_{\mathrm{2D}}^{\perp} 
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the fundamental electronic bandgap and
$\hat{\delta}_{\mathrm{2D}}$ is the intrinsic thickness of the 2D
layer, with coefficients
$C^{\parallel} = {\displaystyle \frac{2 \pi}{Ne^2}}$
\cite{Jiang_2017_Eg_Eb}, where $N$ is a pre-factor associated with the
band degeneracy, and $C^{\perp} = {\varepsilon_{0}}^{-1}$. It is worth
noting, unlike the parameter $\delta_{\mathrm{2D}}$ that is
artificially assigned within the EDM picture (see previous section),
$\hat{\delta_{\mathrm{2D}}}$ can be uniquely defined by
$\alpha_{\mathrm{2D}}^{\parallel}$, a quantity that can be
computationally and experimentally determined. Despite of the
simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp},
they generalize direct relationships between the electronic polarizability and
the electronic / structural properties for any 2D material in a new
framework.

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS\textsubscript{2} in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha_{\mathrm{2D}}^{\parallel}$ and
  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.
  % HSE06 functional is used in all plots.
}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\linewidth]{img/fig-emt-uncertainty.pdf}
  \caption{\label{fig-emt} \textbf{Failure of the effective 2D
      ``dielectric constant'' picture based on the effective medium
      theory (EMT)}. \textbf{a}.  Scheme of the EMT picture where an
    effective 2D ``dielectric constant'' $\varepsilon_{\mathrm{2D}}$
    is extracted from $\varepsilon_{\mathrm{SL}}$, which depends on
    the thickness $\delta_{\mathrm{2D}}$ of the 2D material that is
    not well-defined. \textbf{b}.  Estimation error between
    $\delta_{\mathrm{2D}}^{\parallel, \text{fit}}$ and
    $\delta_{\mathrm{2D}}^{\perp, \text{fit}}$ from non-linear fitting
    of \textit{ab initio} $\varepsilon_{\mathrm{SL}} - L$ data for selected
    2D TMDCs. The uncertainty of
    $\delta_{\mathrm{2D}}$ causes considerable variation of estimated
    $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{c}.) and in
    particular $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{d}.).  }
\end{figure}

>>>>

%
%
Using these relations, we show the calculated
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the selected TMDCs as a function of $L$ in the bottom panels of
Figure \ref{fig-1}b and \ref{fig-1}c, respectively.  In contrast to
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$, We observe that both
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
reach convergence when $L$ exceeds 10 \AA and 15 \AA,
respectively. Such result is in good agreement with the spatially
localized induced dipole moment of a 2D materials as shown in
Supplementary Figure~\ref{SI-fig:rho-profile}.
%
%
% Interestingly, we can use Eqs.\ref{eq:alpha-para-def} and
% \ref{eq:alpha-perp-def} to reproduce the trends noticed in the top
% panels in Figure\ref{fig-1}{\textbf b} and \ref{fig-1}{\textbf c} for
% $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
% $\varepsilon_{\mathrm{SL}}^{\perp}$ as a function of $L$ around a
% centered magnitude of $\alpha_{\mathrm{2D}}^{\parallel}$ and
% $\alpha_{\mathrm{2D}}^{\perp}$
% (Figure \ref{fig-1}\textbf{d}-\textbf{e}).
% A similar curve profile is obtained in both components of the dielectric constant including the much 
% abrupt variation of $\varepsilon_{\mathrm{SL}}^{\perp}$ with $L$ which is due to 
% interlayer interactions.
%\todo[inline]{The original claim of this sentence, that $\varepsilon_{\mathrm{SL}}^{\perp}$ varies more due to interlayer interactions is not 100\% true. I think it is better not to explicitly mention this.}
Such relations can also be used to remove the dependence on $L$ for
frequency-dependent $\varepsilon^{\parallel}_{\mathrm{SL}}(\omega)$
and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, generating
lattice-independent electronic polarizability
$\alpha^{\parallel}_{\mathrm{SL}}(\omega)$ and
$\alpha^{\perp}_{\mathrm{SL}}(\omega)$ in the frequency domain,
respectively (details see Supplementary Section \ref{SI-ssec:gw}).
%
% 
% 
% 
% 
These findings indicate that the electronic polarizability $\alpha_{\mathrm{2D}}$ captures the essence
of the dielectric properties of 2D materials. In contrast to the ill-defined macroscopic $\varepsilon_{\mathrm{SL}}$, $\alpha_{\mathrm{2D}}$ has unique definition, and does not suffer from the dependency on the lattice size.
More discussions about the choice of the
2D polarizability, comparison with other methods, simulations at the
frequency-dependent domain can be found in Supplementary Section
\ref{SI-ssec:gw}.

@@

Apart from the 2D electronic polarizability proposed here, it is worth
mentioning that the effective dielectric model (EDM) is widely used in
literature to treat the 2D material as a slab with an effective
dielectric tensor $\varepsilon_{\mathrm{2D}}$ and thickness
$\delta^{*}_{\mathrm{2D}}$. Such method can be found in both
experimental and theoretical studies, such as to interpret
ellipsometry data
\cite{graphene-epsilon10,Duesberg14,Chiang13,Kong14}, reflectance /
transmission spectra \cite{Li_2014, Yoffe-Wilson69}, optical
conductance \cite{Matthes_2016} and many-body interactions
\cite{Sohier_2016,Meckbach_2018} of 2D materials. The EDM allows
applying physical laws of bulk systems directly to 2D materials using
$\varepsilon_{\mathrm{2D}}$. However, there are several drawbacks of
such approach, first of all, the wavevector($q$)-dependency of
dielectric screening in 2D
sheets~\cite{Cudazzo_2011_screening_2D,Olsen_2016_hydrogen,Trolle_2017_eps_subst}
is not captured. More severely, here we show that, due to the
uncertainty of $\delta^{*}_{\mathrm{2D}}$, the calculated
$\varepsilon_{\mathrm{2D}}$, in particular its out-of-plane component,
is extremely sensitive to the choice of $\delta^{*}_{\mathrm{2D}}$,
making such model questionable.

The basic assumption of EDM can be
seen in the inset of Figure~\ref{fig-1}\textbf{e}, where the macroscopic
$\varepsilon_{\mathrm{SL}}$ is considered to be contributed by (i) a
2D slab with effective dielectric constant $\varepsilon_{\mathrm{2D}}$
and thickness $\delta^{*}_{\mathrm{2D}}$ and (ii) vacuum spacing with
distance $L-\delta^{*}_{\mathrm{2D}}$. Using the effective medium theory
(EMT)~\cite{Aspnes_1982,Markel_2016}, the relation between
$\varepsilon_{\mathrm{SL}}$ and $\varepsilon_{\mathrm{2D}}$ can be
expressed using capacitance-like
equations~\cite{Matthes_2016,Laturia_2018} :
\begin{subequations}
  \begin{eqnarray}
    \label{eq:emt-1}
    {\displaystyle \varepsilon_{\mathrm{SL}}^{\parallel}} &= {\displaystyle \frac{\delta^{*}_{\mathrm{2D}}}{L} \varepsilon_{\mathrm{2D}}^{\parallel} + \left(1 - \frac{\delta^{*}_{\mathrm{2D}}}{L} \right)}\\
     \label{eq:emt-2}
    {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}} &= {\displaystyle \frac{\delta^{*}_{\mathrm{2D}}}{L} \frac{1}{\varepsilon_{\mathrm{2D}}^{\perp}} + \left(1 - \frac{\delta^{*}_{\mathrm{2D}}}{L} \right)}
  \end{eqnarray}
\end{subequations}
In principle, both the values of $\varepsilon_{\mathrm{2D}}$ and
$\delta^{*}_{\mathrm{2D}}$ are unknown for a certain 2D material. To
minimize the modeling error, we used non-linear least-square fitting
to extract $\varepsilon_{\mathrm{2D}}$ and $\delta^{*}_{\mathrm{2D}}$ of
selected 2H TMDCs simultaneously from \textit{ab initio}
$\varepsilon_{\mathrm{SL}}$ -- $L$ data in
Figure~\ref{fig-1}\textbf{b} and \ref{fig-1}\textbf{c} (details see
Supplementary Figure~\ref{SI-fig:rescale-prb}). The fitted values of
the slab thickness, $\delta_{\mathrm{2D}}^{\parallel, \mathrm{fit}}$
and $\delta_{\mathrm{2D}}^{\perp, \mathrm{fit}}$ from in-plane and
out-of-plane data, respectively, are shown in Supplementary
Table~\ref{SI-tab:delta-L-DFt}.
%
% As seen in Figure
% \ref{fig-emt}\textbf{b}, the estimation error of the thickness
% estimated from different directions is around 0.06$\sim{}$0.27
% \AA{}.
%
Although the uncertainty only corresponds to several percent of the
interlayer spacing in the bulk counterparts of these 2D materials, its
influence on the calculated values
$\varepsilon_{\mathrm{2D}}^{\parallel}$ and
$\varepsilon_{\mathrm{2D}}^{\perp}$ is significant. We estimated the
dispersion of $\varepsilon_{\mathrm{2D}}^{\parallel}$ and
$\varepsilon_{\mathrm{2D}}^{\perp}$ if $\delta^{*}_{\mathrm{2D}}$
deviates from the best fitted value by $\pm{}$2.5 \AA{}, as shown in
Figures \ref{fig-1}\textbf{d} and \ref{fig-1}\textbf{e},
respectively. $\varepsilon_{\mathrm{2D}}^{\parallel}$ decays linearly
with $\delta^{*}_{\mathrm{2D}}$,
while strikingly, the value $\varepsilon_{\mathrm{2D}}^{\perp}$ spans
over more than one order of magnitude. The sensitivity of
$\varepsilon_{\mathrm{2D}}^{\perp}$ to $\delta^{*}_{\mathrm{2D}}$
explains the discrepancy in literature that both
isotropic~\cite{Sohier_2016} and highly
anisotropic~\cite{Matthes_2016,Laturia_2018}
$\varepsilon_{\mathrm{2D}}$ tensors for 2D materials under the EDM are
reported. As a consequence, the estimated values of
$\varepsilon_{\mathrm{2D}}$, in particular its out-of-plane component,
is highly questionable.

On the contrary, the proposed $\alpha_{\mathrm{2D}}$ approach does not
suffer from such deficiencies, despite its relatively simple
formalism. The relative uncertainty of $\alpha_{\mathrm{2D}}$ is
generally at the order of 10\textsuperscript{-4} (Supplementary
Figure~\ref{SI-fig:alpha-converg}). In addition, the calculation of
$\alpha_{\mathrm{2D}}$ technically simpler than
$\varepsilon_{\mathrm{2D}}$: (i) $\alpha_{\mathrm{2D}}$ can be
achieved using single-point calculation of macroscopic dielectric
tensor, while $\varepsilon_{\mathrm{2D}}$ requires non-linear fitting
of multiple $\varepsilon_{\mathrm{SL}}$ -- $L$ data points; (ii) the
values of $\alpha_{\mathrm{2D}}$ typically converge well for large $L$
($>$20 \AA{}), while $\varepsilon_{\mathrm{2D}}$ suffers from the
uncertainty as described above.

@@

For bulk materials, pioneering works from the 1950s have demonstrated
empirical equations between $\varepsilon$ and the bandgap
$E_{\mathrm{g}}$, including the
Moss~\cite{Moss_1950_relation,Moss_1985_n_Eg,Finkenrath_1988} or
Ravindra~\cite{Ravindra_1980_model,Ravindra_1979_eps_Eg} relations.
Such universal relations, if exist in the context of
$\alpha_{\mathrm{2D}}$, would be of high importance for studying and
predicting the screening of 2D materials.  Inspired by the random
phase approximation (RPA) theory \cite{Adler_1962} within the
$\mathbf{k} \cdot \mathbf{p}$
formalism\cite{kittel_2005_introduction,Jiang_2017_Eg_Eb}, we propose the universal relations for $\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$,
depending on the electronic and geometric information of a 2D material (see
Supplementary Section \ref{SI-sec:theory-1} for details):
% \begin{subequations}
% \begin{eqnarray}
% \label{eq:2D-Moss-para}
  % &\alpha_{\mathrm{2D}}^{\parallel} &=C^{\parallel} E_{g}^{-1} \\
  % \label{eq:2D-Moss-perp}
  % &\alpha_{\mathrm{2D}}^{\perp} & =C^{\perp} \hat{\delta}_{\mathrm{2D}}
% \end{eqnarray}
% \end{subequations}
\begin{subequations}
\begin{eqnarray}
\label{eq:2D-Moss-para}
  &E_{\mathrm{g}} &= C^{\parallel} \alpha_{\mathrm{2D}}^{\parallel} \\
  \label{eq:2D-Moss-perp}
  &\hat{\delta}_{\mathrm{2D}} & = C^{\perp} \alpha_{\mathrm{2D}}^{\perp} 
\end{eqnarray}
\end{subequations}
where $E_{\mathrm{g}}$ is the fundamental electronic bandgap and
$\hat{\delta}_{\mathrm{2D}}$ is the intrinsic thickness of the 2D
layer, with coefficients
$C^{\parallel} = {\displaystyle \frac{2 \pi}{Ne^2}}$
\cite{Jiang_2017_Eg_Eb}, where $N$ is a pre-factor associated with the
band degeneracy, and $C^{\perp} = {\varepsilon_{0}}^{-1}$. It is worth
noting, unlike the parameter $\delta^{*}_{\mathrm{2D}}$ that is
artificially assigned within the EDM picture (see previous section),
$\hat{\delta^{*}_{\mathrm{2D}}}$ can be uniquely defined by
$\alpha_{\mathrm{2D}}^{\parallel}$, a quantity that can be
computationally and experimentally determined. Despite of the
simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp},
they generalize direct relationships between the electronic polarizability and
the electronic / structural properties for any 2D material in a new
framework.

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[H]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
\caption{\label{fig-1} \textbf{2D polarizability and the breakdown of
    effective dielectric model
    (EDM)} % \textbf{2D polarizability as the
  % true descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS\textsubscript{2} in a periodic superlattice under
  external eletric field of 0.01 V/\AA{}.  The green and red regions
  represent negative and positive induced charges, respectively. The
  macroscopic $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities
  $\alpha_{\mathrm{2D}}^{\parallel}$ and
  $\alpha_{\mathrm{2D}}^{\perp}$ are invariant with lattice size
  \textbf{b}.  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{2D}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{2D}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. On the other hand, the EDM approach
  which usually used in literature to extract the effective 2D
  dielectric constant $\varepsilon_{\mathrm{2D}}$, fails to produce
  consistent results, estimation uncertainty of the effective layer
  thickness $\delta^{*}_{\mathrm{2D}}$, causes huge variations of
  $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{d}) and
  $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{e}).
  % HSE06 functional is used in all plots.
}
\end{figure}

% \begin{figure}[H]
%   \centering
%   \includegraphics[width=0.75\linewidth]{img/fig-emt-uncertainty.pdf}
%   \caption{\label{fig-emt} \textbf{Failure of the effective 2D
%       ``dielectric constant'' picture based on the effective medium
%       theory (EMT)}. \textbf{a}.  Scheme of the EMT picture where an
%     effective 2D ``dielectric constant'' $\varepsilon_{\mathrm{2D}}$
%     is extracted from $\varepsilon_{\mathrm{SL}}$, which depends on
%     the thickness $\delta_{\mathrm{2D}}$ of the 2D material that is
%     not well-defined. \textbf{b}.  Estimation error between
%     $\delta_{\mathrm{2D}}^{\parallel, \text{fit}}$ and
%     $\delta_{\mathrm{2D}}^{\perp, \text{fit}}$ from non-linear fitting
%     of \textit{ab initio} $\varepsilon_{\mathrm{SL}} - L$ data for selected
%     2D TMDCs. The uncertainty of
%     $\delta_{\mathrm{2D}}$ causes considerable variation of estimated
%     $\varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{c}.) and in
%     particular $\varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{d}.).  }
% \end{figure}
